Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-16 docs/paper/paper.tex
Updated major comparison to firefox 41 nightly

\begin{table}
  \centering
  \begin{tabular}{|l|l|}
    \hline
    Computer & Mac Book Air \\
    Processor & Intel Core i5 \\
    Clock Frequency & 1.8 GHz \\
    System Memory & 4 GB \\
    Operating System & OS X Yosemite 10.10.3 \\
    Browser version & Firefox Nightly 40.0a1 \\
    \hline
  \end{tabular}
  \caption{Benchmarks environment.}
  \label{tab:env}
\end{table}

@@

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{154442} & 377.2\\
    1,000 & \textbf{17460.2} &  368.4 \\
    10,000 & \textbf{1768.6} & 311.2 \\
    100,000 & \textbf{179.2} & 172.2 \\
    1,000,000 & 16.96 & \textbf{33.2} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

\begin{figure}
\centering
\includegraphics[height=8.2cm]{comparison}
\caption{Relative performance of parallel transformation compared to sequential one.}
\label{fig:relative}
\end{figure}

>>>>

\begin{table}
  \centering
  \begin{tabular}{|l|l|}
    \hline
    Computer & Mac Book Air \\
    Processor & Intel Core i5 \\
    Clock Frequency & 1.8 GHz \\
    System Memory & 4 GB \\
    Operating System & OS X Yosemite 10.10.3 \\
    Browser version & Firefox Nightly 41.0a1 \\
    \hline
  \end{tabular}
  \caption{Benchmarks environment.}
  \label{tab:env}
\end{table}

@@

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{142223} & 328 \\
    1,000 & \textbf{16503.8} &  359 \\
    10,000 & \textbf{1683.8} & 321.8 \\
    100,000 & \textbf{169.6} & 184.4 \\
    1,000,000 & 16.8 & \textbf{34.1} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

\begin{figure}
\centering
\includegraphics[height=7.7cm]{comparison}
\caption{Relative performance of parallel transformation compared to sequential one.}
\label{fig:relative}
\end{figure}
